The Splashback Radius of Planck-SZ clusters

### 2018-12-13 Paper_v2/RSP_paper_new.tex
Adding second version of paper

Given the mass of the halo, the location of the splashback radius
constitutes a direct probe of the halo accretion rate. Motivated by
these studies, \citet{more2016detection} attempted to detect this
feature in observations. Using the optically selected Sloan Digital
Sky Survey RedMaPPer galaxy cluster catalog
\citep{rykoff2014redmapper}, and by cross-correlating it with the
SDSS photometric galaxy sample, \citet{more2016detection} found evidence
for the steepening of the dark matter density profile, and therefore
the splashback radius of this sample of galaxy clusters. This was 
corroborated by including further models for mis-centering by
\citet{baxter2017halo} and in the Dark Energy Survey data by
\citet{chang2017splashback} using optically selected clusters. Somewhat surprisingly,
\citet{more2016detection} found that the location of the splashback radius was
inconsistent with that expected from numerical simulations of dark matter by
about $20\pm5$\% (see also \citet{baxter2017halo, chang2017splashback}).
Although they
investigated potential systematic issues, they did not have access
to mock cluster catalogs which could mimic the selection effects of
optically-identified clusters. \citet{busch2017assembly} used a
simplified optical cluster selection algorithm on the Millennium
simulation, and pointed out that optical clusters can be heavily
affected by projection issues, and could potentially introduce
systematics in the inference of the splashback radius, as well as
halo assembly bias. The existence of projection effects in the
optical cluster catalog in the context of halo assembly bias was 
also demonstrated by \citet{zu2016level}.

\citet{umetsu2017lensing} as well as \citet{contigiani2018weak}
recently used Xray selected clusters to look for the splashback radius
using the weak lensing signal, however stacking issues and the low
signal-to-noise ratio remains a significant hurdle for both of them.
\citet{chang2017splashback} found evidence for the splashback radius
in the weak lensing signal, but their analysis was again done using
optically selected clusters in the Dark energy survey. Regardless of the
projection issues present in the optical cluster catalog, there is some
inherent circularity present in the logic of using photometric galaxies to
select clusters as over-densities in a given aperture, and then using the same
photometric sample of galaxies to look for the splashback radius. There is a
possibility that the aperture used to select the cluster catalogs could be
imprinted in a non-trivial way on the measured number density profiles of
clusters.

In this work, we move away from the optical cluster selection and
explore the use of SZ selected cluster catalogs. While the SZ
selected clusters can also be susceptible to systematic selection
effects, the scales on which the SZ signal is measured and the
cluster selection is performed is much smaller than the expected
location of the splashback radius (typically $R_{\rm 500c}$). We use
this sample to explore the evidence for the splashback radius in
observations.  Due to the low signal-to-noise ratio of the weak
lensing signal, we perform our analysis using cross-correlation of
galaxies with clusters.  The SDSS sample used by
\citet{more2016detection} was deep enough such that biases in the
location of the splashback radius due to dynamical friction effects
were expected to be small.  Nevertheless, we use galaxy samples, which
are even fainter by $0.5-1$ magnitudes compared to those used by
\citet{more2016detection}.

@@

\begin{figure}
    \includegraphics[scale=0.55]{Planck_summary.pdf}
\caption{The distribution of the masses and redshifts of the galaxy clusters
from the PSZ2 catalog that we use in our analysis. The histograms on the right
hand side and the bottom show the distribution in mass and redshift,
respectively.}
   \label{fig:planck_summary}
\end{figure}

The baryonic component of a galaxy cluster is dominated by the hot,
ionized  intra-cluster medium (ICM), which is gravitationally bound
within the cluster. The cosmic microwave background (CMB) photons
that pass through the cluster inverse Compton scatter off the hot
electrons and gain energy. This effect is known as the thermal
Sunyaev-Zeldovich (SZ) effect
\citep{sunyaev1970small,sunyaev1980velocity}. The effect has a
characteristic frequency dependence and results in an intensity
decrease below 220 GHz and an associated increase at higher
frequencies. The multiple frequency channels on the Planck satellite
allow a detection of galaxy clusters using the SZ effect
\citep{collaboration2016planck}. As part of the 2015 Data Release of
the Planck mission, the second Planck Catalogue of Sunyaev-Zeldovich
Sources (PSZ2) was made available to the community. The PSZ2 catalog
contains detections based on  three different techniques
\citep{ade2016planck}, and the union of these catalogs has in total
1653 galaxy clusters, of which 1203 clusters have been confirmed by
cross-matching to other galaxy clusters from external data sets. 
\begin{table}
    \centering
    \caption{Comparison of the PSZ2 cluster catalog
    against the RedMaPPer cluster catalog used by
\citet{more2016detection}. The values of the mass estimates
$M_{\mathrm{500c}}$, $M_{\mathrm{200m}}$, redshifts $z$ and expected
splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ represent the
catalog averages. The redshifts for both catalogs are given from the
survey. For the RedMaPPer catalog the $M_{\mathrm{200m}}$ mass
estimates were obtained from gravitational lensing and for the PSZ2
catalog the $M_{\mathrm{500c}}$ estimates were calculated from the
survey parameters using the scaling relation between the integrated
Compton Y-parameter $Y_{500c}$ and $M_{500c}$ as found by
\citet{ade2014planck}. The missing mass estimates as well as the
expected values of the splashback radii were calculated using the
Python package COLOSSUS \citep{diemer2017colossus}. The predictions
for the splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ are
given in comoving units.}
    \label{tab:cluster_catalogs} 
    \begin{tabular}{ccc}
    \hline 
    & RedMaPPer & PSZ2 \\
    \hline 
    $z$ & 0.24 & 0.177 \\
    \hline 
    \# objects & 8643 & 596\\
    \hline
    $M_{\mathrm{500c}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 0.9 & 3.0 \\
    \hline
    $M_{\mathrm{200m}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 1.8 & 6.2\\ 
    \hline
    $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ [$h^{-1}$ Mpc] & 1.37 & 1.89 \\
    \hline
    \end{tabular} 
\end{table}
\begin{table*}
    \centering
    \caption{Summary and comparison of the properties of the galaxy catalogs used in this work as well as the SDSS catalog used in \citet{more2016detection}.}
    \label{tab:galaxy_catalogs}
    \begin{tabular}{ccccc}
    \hline 
    & SDSS & PS 21 & PS 21.5 & PS 22 \\ 
    \hline 
    depth [mag] & 21.00 & 21.00 & 21.50 & 22.00\\ 
    \hline 
    eff. area [deg$^2$] & $\approx$ 10'000 & 21'148 & 20'586 & 15'689\\ 
    \hline 
    \# objects & 57'181'113 & 93'772'329 & 123'188'529 & 105'809'113 \\
    \hline
    objects/deg$^2$ & 5718 & 4434 & 5984 & 6744\\ 
    \hline
    \end{tabular} 
\end{table*}
\begin{table*}
    \centering
    \caption{Summary of the priors used in the MCMC sampling
procedure. The MCMC chains are constrained using flat priors or
normal priors on some of the fitting parameters. This table lists
the ranges of the flat priors and the central positions as well as
the scales of the normal priors ( format: center | scale ),
respectively.}
    \label{tab:priors}
    \begin{tabular}{ccccccccc}
    \hline 
    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
    \hline 
    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 
    \hline 
    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\
    \hline
    \end{tabular} 
\end{table*}

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in order to
have a similar redshift range used in \citet{more2016detection}. The mass and
the redshift distribution of the Planck clusters we use is shown in
Fig.~\ref{fig:planck_summary}. Due to the larger beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this assumption, we additionally 
study the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Appendix~\ref{sec:mis-centering}).

The final sample that we use consists of 596
galaxy clusters and is about an order of magnitude smaller compared
to the sample used in \citet{more2016detection}. The sample we use
in this paper has an average redshift of 0.177, and an average
cluster mass $M_{500c}$ of about $3.0 \times 10^{14}
h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
the main properties of the cluster catalog used in this work to that
used by \citet{more2016detection}. Additionaly, Figure~\ref{fig:planck_summary}
visualizes the distribution of the masses and redshifts of the used clusters.
A map of the sky positions of the clusters
can be found in Figure~\ref{fig:planck_fig} in
Appendix~\ref{sec:figures}.

@@

As mentioned in the description of the Pan-STARRS survey by
\citet{chambers2016pan} there is a significant variation in the
depth of the 3$\pi$ Steradian survey even on small scales. In order
to avoid choosing objects in shallow regions of the survey the
maximum observed Kron magnitude in the $i_{\mathrm{P1}}$ band in
each \textit{skycell} is recorded and only objects in skycells with
a maximum observed Kron magnitude of 21.0, 21.5 and 22.0 or brighter
are selected depending on the corresponding catalog. Since most of
the shallow regions lie in the galactic plane, we mask out the
region at low galactic latitudes $|b|<20\degr$. The resultant
HEALPix maps showing the excluded areas on the sky can be found in
Figure~\ref{fig:heal_map}. We further disregard objects in bad
pixel regions as indicated by the $i_{\mathrm{P1}}$ band
\textit{stack.mask} images.

@@

Therefore the model is described by eight model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function to the measured two-dimensional correlation signal. 
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}. We adopt priors similar to
\citet{more2016detection} on some of our parameters based on the
expectations of their values from numerical simulations, but double
the scales of the normal priors compared to their work (see
Table~\ref{tab:priors}). The central value for the prior on $\alpha$
is deduced from mass estimates \citep{gao2008redshift}, whereas the
central values on the priors of $\beta$ and $\gamma$ were
recommended by \citet{diemer2014dependence}.

The splashback radius for halos on galaxy cluster scales is consistent
with the location of the steepest logarithmic slope of the density
profile. We estimate the steepest slope of both the two-dimensional
and the three-dimensional cross-correlation function. The
locations of the steepest slope in the two-dimensional and the
three-dimensional case are expected to be different by
about 20\% for typical cluster halo parameters
\citep{diemer2014dependence, more2016detection}.

@@

\section{Results}
\label{sec:Results}
\subsection{Cluster-galaxy cross-correlations}
The measurements of the two-dimensional cluster-galaxy
cross-correlations are shown as black points with error bars in the
left column of Figure~\ref{fig:2D_graphs}. The different rows
correspond to the three different absolute magnitude limits that we
have used to select all the galaxies when calculating the
cross-correlations. The cross-correlation signal is clearly detected
in all three measurements and the corresponding signal-to-noise
ratios of the measurements are listed in Table~\ref{tab:snr}.

We fit these measurements with our parametric model in Equation~\ref{eq:surface}
and compute the posterior distribution of the model parameters 
as described in Section~\ref{sec:estimators}. The
median of the MCMC fit is indicated by the central solid line, while
the shaded area marks the 68\% credible interval for the fit. The
median values of the posterior distributions of the parameters along
with their 68\% confidence intervals are listed in
Table~\ref{tab:fit_parameters} along with the corresponding reduced
$\chi^2$ values for the best fit. The two-dimensional posterior
distributions for each pair of parameters are shown in
Figures~\ref{fig:corner_21}, \ref{fig:corner_21.5} and
\ref{fig:corner_22} for the three absolute magnitude limits,
respectively.

\begin{figure}
    \includegraphics[scale=0.65]{2D_graphs_with_spline_no_mc.pdf}
\caption{The estimates of the two-dimensional cross-correlation
signals (black dots) are shown in the left column. The colored
curves show the two-dimensional model fits of the functional
form in Equation~\ref{eq:surface}. The magnitude limit applied to the galaxy
catalog is indicated in each row along with the signal-to-noise ratio (SNR). 
The vertical, shaded regions indicate the estimates of the locations of 
steepest slope of the profiles as estimated from the corresponding minima of the
derivative profiles, which are shown in the right column. For
comparison, the location of the $r_{\mathrm{200m}}$ radius as
calculated from the average cluster sample properties is indicated
by the black, dotted lines.}
   \label{fig:2D_graphs}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[scale=0.85]{3D_graphs_with_spline_no_mc.pdf}
\caption{The estimates of the three-dimensional cross-correlation
signals are shown in the leftmost column. The colored curves show the
model fits of the functional form in Equation~\ref{eq:model}. The magnitude
limit applied on the galaxy catalog is indicated in each row along with 
the signal-to-noise ratio (SNR). The vertical, shaded regions indicate the 
estimates of the splashback radii as estimated from the corresponding minima 
of the derivative profiles, which are shown in the column in the middle. The
rightmost column shows the second derivative profiles in matching color.
The grey curves show the corresponding, estimated first and second derivatives of the 
one-halo term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:dk14}).
For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated 
from the average cluster sample properties is indicated by the black, dotted
lines.}
   \label{fig:3D_graphs} 
\end{figure*}

\begin{table}
    \centering
    \caption{We list the signal to noise ratios (SNRs) of our
different estimates of the two-dimensional cross-correlation
obtained by using the different galaxy samples. For comparison: The SNR
achieved by \citet{more2016detection} is 263. It is much higher
due to size of the cluster sample used in their study.}
    \label{tab:snr}
    \begin{tabular}{cccc}
    \hline
    gal cat & PS 21 & PS 21.5 & PS 22 \\ 
    \hline
    \hline
   SNR & 42.4 & 43.3 & 30.9 \\
    \hline
    \end{tabular} 
\end{table}

>>>>

Given the mass of the halo, the location of the splashback radius
constitutes a direct probe of the halo accretion rate. Motivated by
these studies, \citet{more2016detection} attempted to detect this
feature in observations. Using the optically selected Sloan Digital
Sky Survey RedMaPPer galaxy cluster catalog
\citep{rykoff2014redmapper}, and by cross-correlating it with the
SDSS photometric galaxy sample, \citet{more2016detection} found evidence
for the steepening of the dark matter density profile, and therefore
the splashback radius of this sample of galaxy clusters. This was 
corroborated by including further models for mis-centering by
\citet{baxter2017halo} and in the Dark Energy Survey data by
\citet{chang2017splashback} using optically selected clusters. Somewhat surprisingly,
\citet{more2016detection} found that the location of the splashback radius was
inconsistent with that expected from numerical simulations of dark matter by
about $20\pm5$\% (see also \citet{baxter2017halo, chang2017splashback}).
Although they
investigated potential systematic issues, they did not have access
to mock cluster catalogs which could mimic the selection effects of
optically-identified clusters. \citet{busch2017assembly} used a
simplified optical cluster selection algorithm on the Millennium
simulation, and pointed out that optical clusters can be heavily
affected by projection issues, and could potentially introduce
systematics in the inference of the splashback radius, as well as
halo assembly bias. The existence of projection effects in the
optical cluster catalog in the context of halo assembly bias was 
also demonstrated by \citet{zu2016level}. Regardless of the
projection issues present in the optical cluster catalog, there is some
inherent circularity present in the logic of using photometric galaxies to
select clusters as over-densities in a given aperture, and then using the same
photometric sample of galaxies to look for the splashback radius. There is a
possibility that the aperture used to select the cluster catalogs could be
imprinted in a non-trivial way on the measured number density profiles of
clusters.

\textbf{Trying to avoid the problems which complicate the unbiased detction
of the splashback signal in opical samples some recent studies searched
for the signature of the splashback effect using non-optical cluster samples.}
\citet{umetsu2017lensing} as well as \citet{contigiani2018weak}
used Xray selected clusters to look for the splashback radius
using the weak lensing signal, however stacking issues and the low
signal-to-noise ratio remains a significant hurdle for both of them.
Also \citet{chang2017splashback} found evidence for the splashback feature
in the weak lensing signal, but their analysis was again done using
optically selected clusters in the Dark energy survey suffering from 
the before mentioned issus again.

\textbf{In this work, we explore yet another non-optical cluster sample. 
Namely, SZ selected clusters.} While the SZ
selected clusters can also be susceptible to systematic selection
effects, the scales on which the SZ signal is measured and the
cluster selection is performed is much smaller than the expected
location of the splashback radius (typically $R_{\rm 500c}$). We use
this sample to explore the evidence for the splashback radius in
observations.  Due to the low signal-to-noise ratio of the weak
lensing signal, we perform our analysis using cross-correlation of
galaxies with clusters.

\textbf{Dynamcial friction is expected to decrease the observed splashback radius in 
massive clusters. It causes a
slow-down of the massive subhalos, hosting many of the observed galaxies, 
which in return decreases the apocentric
radius of their orbits and therefore the measured splashback radius of the host cluster. 
Since the rate of dynamical friction scales
with the mass of the moving object the effect is stronger for more
massive subhalos. Therefore, one expects the decrease in the splashback
radius to scale with the amount of massive subhalos in the host cluster and
with its mass \citep{adhikari2016observing}. This bias can be limited by choosing a deep enough
galaxy sample such that a large enough amount of low mass subhalos can be
observed.} The SDSS sample used by
\citet{more2016detection} was already deep enough such that biases in the
location of the splashback radius due to dynamical friction effects
were expected to be small. 
Nevertheless, we use galaxy samples, which
are even fainter by $0.5-1$ magnitudes compared to those used by
\citet{more2016detection}.

@@

The baryonic component of a galaxy cluster is dominated by the hot,
ionized  intra-cluster medium (ICM), which is gravitationally bound
within the cluster. The cosmic microwave background (CMB) photons
that pass through the cluster inverse Compton scatter off the hot
electrons and gain energy. This effect is known as the thermal
Sunyaev-Zeldovich (SZ) effect
\citep{sunyaev1970small,sunyaev1980velocity}. The effect has a
characteristic frequency dependence and results in an intensity
decrease below 220 GHz and an associated increase at higher
frequencies. The multiple frequency channels on the Planck satellite
allow a detection of galaxy clusters using the SZ effect
\citep{collaboration2016planck}. As part of the 2015 Data Release of
the Planck mission, the second Planck Catalogue of Sunyaev-Zeldovich
Sources (PSZ2) was made available to the community. The PSZ2 catalog
contains detections based on  three different techniques
\citep{ade2016planck}, and the union of these catalogs has in total
1653 galaxy clusters, of which 1203 clusters have been confirmed by
cross-matching to other galaxy clusters from external data sets. 
\begin{table}
    \centering
    \caption{Comparison of the PSZ2 cluster catalog
    against the RedMaPPer cluster catalog used by
\citet{more2016detection}. The values of the mass estimates
$M_{\mathrm{500c}}$, $M_{\mathrm{200m}}$, redshifts $z$ and expected
splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ represent the
catalog averages. The redshifts for both catalogs are given from the
survey. For the RedMaPPer catalog the $M_{\mathrm{200m}}$ mass
estimates were obtained from gravitational lensing and for the PSZ2
catalog the $M_{\mathrm{500c}}$ estimates were calculated from the
survey parameters using the scaling relation between the integrated
Compton Y-parameter $Y_{500c}$ and $M_{500c}$ as found by
\citet{ade2014planck}. The missing mass estimates as well as the
expected values of the splashback radii were calculated using the
Python package COLOSSUS \citep{diemer2017colossus}. The predictions
for the splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ are
given in comoving units.}
    \label{tab:cluster_catalogs} 
    \begin{tabular}{ccc}
    \hline 
    & RedMaPPer & PSZ2 \\
    \hline 
    $z$ & 0.24 & 0.177 \\
    \hline 
    \# objects & 8643 & 596\\
    \hline
    $M_{\mathrm{500c}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 0.9 & 3.0 \\
    \hline
    $M_{\mathrm{200m}}$ [$h^{-1}10^{14} $M$_{\sun}$] & 1.8 & 6.2\\ 
    \hline
    $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ [$h^{-1}$ Mpc] & 1.37 & 1.89 \\
    \hline
    \end{tabular} 
\end{table}
\begin{table*}
    \centering
    \caption{Summary and comparison of the properties of the galaxy catalogs used in this work as well as the SDSS catalog used in \citet{more2016detection}.}
    \label{tab:galaxy_catalogs}
    \begin{tabular}{ccccc}
    \hline 
    & SDSS & PS 21 & PS 21.5 & PS 22 \\ 
    \hline 
    depth [mag] & 21.00 & 21.00 & 21.50 & 22.00\\ 
    \hline 
    eff. area [deg$^2$] & $\approx$ 10,000 & 21,148 & 20,586 & 15,689\\ 
    \hline 
    \# objects & 57,181,113 & 93,772,329 & 123,188,529 & 105,809,113 \\
    \hline
    objects/deg$^2$ & 5718 & 4434 & 5984 & 6744\\ 
    \hline
    \end{tabular} 
\end{table*}

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$ in 
order to have a similar redshift range as used in \citet{more2016detection}. 
Due to the larger beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this assumption, we additionally 
study the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Appendix~\ref{sec:mis-centering}).

The final sample that we use consists of 596
galaxy clusters and is about an order of magnitude smaller compared
to the sample used in \citet{more2016detection}. The sample we use
in this paper has an average redshift of 0.177, and an average
cluster mass $M_{500c}$ of about $3.0 \times 10^{14}
h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
the main properties of the cluster catalog used in this work to that
used by \citet{more2016detection}. Additionaly, Figure~\ref{fig:planck_summary}
visualizes the distribution of the masses and redshifts of the used clusters.
A map of the sky positions of the clusters as well as a visualization of their redshift and mass distributions
can be found in Appendix~\ref{sec:figures}.

@@

As mentioned in the description of the Pan-STARRS survey by
\citet{chambers2016pan} there is a significant variation in the
depth of the 3$\pi$ Steradian survey even on small scales. In order
to avoid choosing objects in shallow regions of the survey the
maximum observed Kron magnitude in the $i_{\mathrm{P1}}$ band in
each \textit{skycell} is recorded and only objects in skycells with
a maximum observed Kron magnitude of 21.0, 21.5 and 22.0 or brighter
are selected depending on the corresponding catalog. Since most of
the shallow regions lie in the galactic plane, we mask out the
region at low galactic latitudes $|b|<20\degr$. The resultant
HEALPix maps showing the excluded areas on the sky can be found in
Appendix~\ref{sec:figures}. We further disregard objects in bad
pixel regions as indicated by the $i_{\mathrm{P1}}$ band
\textit{stack.mask} images.

@@

Therefore the model is described by eight model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function to the measured two-dimensional correlation signal. 
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}. 
\textbf{We keep the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and $s_{\mathrm{e}}$ 
as free parameters during the fitting procedure. Similarly to \citet{more2016detection} 
we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and $\log_{10}(r_{\mathrm{t}})$ but double 
their ranges to $[0.1,5.0]$ compared to their work. In contrast, 
we use a normal prior with a central value of $\log_{10}(0.2)$ and a scale of 1.2 
for $\log_{10}(\alpha)$ as deduced from mass estimates \citep{gao2008redshift}. 
For the parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use normal 
priors with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$, respectively 
and scale 0.4 as recommended by \citet{diemer2014dependence}.}

\textbf{It has been a common concern that the profile in Equation~\ref{eq:model} might introduce
a splashback feature simply by its functional from and without its presence in the data.
However, \citet{baxter2017halo} showed that this is not the case by using a Bayesian odds 
ratio approach to asses that the data is described significantly better by the general 
profile in Equation~\ref{eq:model} (with the splashback feature)
rather than by the same profile with fixed $f_{trans} = 1$ (without splashback feature).
The same conclusion was made by \citet{umetsu2017lensing} who conducted a similar study but
using weak lensing data.}
%\begin{table*}
%    \centering
%    \caption{Summary of the priors used in the MCMC sampling
%procedure. The MCMC chains are constrained using flat priors or
%normal priors on some of the fitting parameters. This table lists
%the ranges of the flat priors and the central positions as well as
%the scales of the normal priors ( format: center | scale ),
%respectively.}
%    \label{tab:priors}
%    \begin{tabular}{ccccccccc}
%    \hline 
%    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}%(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 
%    \hline 
%    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 
%    \hline 
%    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $%\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\
%    \hline
%    \end{tabular} 
%\end{table*}

\textbf{While there have been other suggestions for defining the location of the
splashback radius (see \citet{adhikari2014splashback, shi2016outer, 
mansfield2017splashback, diemer2017splashback}) we adopt the 
definition given by \citet{more2015splashback}, who define
the location of the splashback radius for halos on galaxy cluster scales to 
be consistent with the location of the steepest logarithmic slope of the density
profile, due to its easy accessibility in data.}

We estimate the steepest slope of both the two-dimensional
and the three-dimensional cross-correlation function. The
locations of the steepest slope in the two-dimensional and the
three-dimensional case are expected to be different by
about 20\% for typical cluster halo parameters
\citep{diemer2014dependence, more2016detection}.

@@

\section{Results}
\label{sec:Results}
The measurements of the two-dimensional cluster-galaxy
cross-correlations are shown as black points with error bars in the
first row of Figure~\ref{fig:all_graphs}. The different columns
correspond to the three different absolute magnitude limits that we
have used to select all the galaxies when calculating the
cross-correlations. The cross-correlation signal is clearly detected
in all three measurements. \textbf{The signal to noise ratios of the 
three different estimates of the two-dimensional cross-correlation 
signals amount to 42.4, 43.3 and 30.9 for the galaxy samples PS 21, 
PS 21.5 and PS 22, respectively. For comparison: 
The SNR achieved by \citet{more2016detection} is 263. It is much higher
due to size of the cluster sample used in their study.}

We fit these measurements with our parametric model in Equation~\ref{eq:surface}
and compute the posterior distribution of the model parameters 
as described in Section~\ref{sec:estimators}. The
median of the MCMC fit is indicated by the central solid line, while
the shaded area marks the 68\% credible interval for the fit. The
median values of the posterior distributions of the parameters along
with their 68\% confidence intervals are listed in
Table~\ref{tab:fit_parameters} along with the corresponding reduced
$\chi^2$ values for the best fit.

\textbf{We show the two-dimensional posterior
distributions for each pair of parameters for the PS 21.5 sample in 
Figure~\ref{fig:corner_21.5}. Since the posterior distributions for 
the other datasetsare very similar we refrain from showing them as well. 
It is observed that there are some strong degeneracies present between 
parameters describing the same part of the model in Equation~\ref{eq:model} 
(namely $\rho_{\mathrm{in}}$, $f_{\mathrm{trans}}$ and $\rho_{\mathrm{out}}$).
This is not unexpected since certain combinations of parameter values can 
very well result in the same functional shape of the different parts of 
the model. This degeneracy also leads to some of the parameters not being 
constrained tightly (especially $\rho_s$ and $r_s$ due to their strong degeneracy 
with $\alpha$). On the other hand, it is important to note that there is 
no degeneracy present between parameters describing different parts of the 
model, which means that the overall shape of the profile is well constrained. 
Note also that, since the location of the splashback radius only depends on 
the overall shape of the profile the uncertainties of the individual parameters 
within the independent parts of the profile do not translate
into an uncertainty of the location of the splashback feature directly.}

\begin{figure*}
	\centering{
    \includegraphics[scale=0.85]{MAIN_results_with_spline_no_mc.pdf}}
\caption{The main results of the study are presented in this Figure.
The first two rows show the inferred two-dimensional cross-correlation
signals as well as its derivatives.
The three different columns correspond to the three different galaxy
samples cross-correlated with the cluster sample.
The magnitude limit applied to the galaxy catalog is indicated in 
each tile of the first row along with the signal-to-noise ratio (SNR).
The measurements of the two-dimensional cross-correlation
signals (black dots) are shown in the first row as well. There, the colored
curves show the two-dimensional model fits of the functional
form in Equation~\ref{eq:surface}. The vertical, shaded regions indicate 
the estimates of the locations of steepest slope of the profiles as estimated from the corresponding minima of the two-dimensional
derivative profiles, which are shown in the second row. 
Rows three to five show the corresponding three-dimensional model fit
with the functional form Equation~\ref{eq:model} as well as its first and
second order derivatives.
In rows three to five the vertical, shaded regions indicate the 
estimates of the splashback radii as estimated from the corresponding minima 
of the three-dimensional derivative profiles.
The grey curves show the corresponding, estimated first and second derivatives of the 
one-halo term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:model}).
For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated 
from the average cluster sample properties is indicated by the black, dotted
lines.}
   \label{fig:all_graphs}
\end{figure*}

%\begin{table}
%    \centering
%    \caption{We list the signal to noise ratios (SNRs) of our
%different estimates of the two-dimensional cross-correlation
%obtained by using the different galaxy samples. For comparison: The SNR
%achieved by \citet{more2016detection} is 263. It is much higher
%due to size of the cluster sample used in their study.}
%    \label{tab:snr}
%    \begin{tabular}{cccc}
%    \hline
%    gal cat & PS 21 & PS 21.5 & PS 22 \\ 
%    \hline
%    \hline
%   SNR & 42.4 & 43.3 & 30.9 \\
%    \hline
%    \end{tabular} 
%\end{table}
